Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
update

\maketitle
\begin{abstract}
Social networking sites (SNSs) see a variety of spam and scams targeted at 
their users. In contrast to the more limited amounts of secondary information 
available when analyzing email spam, spam on SNSs is accompanied by a wealth 
of data on the sender, which can be used to build more accurate detection mechanisms. 
We analyze 4 million private messages as well as other public and private data from 
a popular social network in order to gain insight into the various features of 
spam messages and the accompanying user accounts data available to site operators. 
We use these insights to choose features that best differentiate spammers from 
legitimate, ``ham," users.  Finally, we extract these features from the site's data 
and use them to train and evaluate classifiers.
\end{abstract}

@@

Social networks of any significant size witness a constant flow of spam, scams and phishing attacks. 
The nature of this unwanted activity, which we henceforth refer to collectively as ``spam" can be 
quite diverse, specific to a site's target audience and often not trivial to detect. Marketers 
spam members with unwanted advertisements, fraudsters lure users with advance fee frauds and 
other confidence tricks, while others may attempt to steal user information by directing users 
to external phishing pages.

@@

\subsection{Spam Set}

@@

\subsection{Ham Set}

@@

\section{Classification \& Results}

>>>>

\maketitle
\begin{abstract}
Social networking sites (SNSs) see a variety of spam and scams targeted at 
their users. In contrast to the limited amounts of information available beyond 
message text and headers when analyzing email spam, spam on SNSs is often accompanied 
by a wealth of data on the sender, which can be used to build more accurate detection mechanisms. 
We analyze 4 million private messages as well as other public and private data from 
a popular social network in order to gain insight into the various features of 
spam messages and the accompanying user accounts data available to site operators. 
We use these insights to choose features that best differentiate spammers from 
legitimate, ``ham," users.  Finally, we extract these features from the site's data 
and use them to train and evaluate classifiers.
\end{abstract}

@@

Social networks of any significant size witness a constant flow of spam, scams and phishing attacks. 
The nature of this unwanted activity, which we henceforth refer to collectively as ``spam" can be 
quite diverse, specific to a site's target audience and often not easily detectable. Marketers 
spam members with unwanted advertisements, fraudsters lure users with advance fee frauds and 
other confidence tricks, while others may attempt to steal user information by directing users 
to external phishing pages.

@@

\subsection{Spam Data Set}

@@

\subsection{Ham Data Set}

@@

\section{Classifiers \& Results}
